Towards ....

### 2015-03-24 paper/nodalida2015.tex
more text

\date{}

@@

We make each analysis a variable \texttt{v1}--\texttt{v5}. 
For instance, \texttt{v3} is a hypothesis that the correct analysis 
for the word form ``bear'' is \texttt{"bear" n pl}.
Before applying rules, we must make sure that in each position
at least one of the analyses is true. We add our first disjunctions:

\begin{itemize}
\item [] $v1$ \\ $v2 \vee v3$ \\ $v4 \vee v5$
\end{itemize}

@@

@@

% Do not number the acknowledgment section. Do not include this section
% when submitting your paper for review.

>>>>

\date{\today}

@@

We make each analysis a variable; let us call them \texttt{det1}, \texttt{n2}, \texttt{v2}, \texttt{n3} and \texttt{v3} by the proposed POS tag and the position in the sentence.
For instance, \texttt{n2} is a hypothesis that the correct analysis 
for the word form ``bear'' is \texttt{"bear" n pl}.
Before applying rules, we must make sure that in each position
at least one of the analyses is true. We add our first disjunctions:

\begin{itemize}
\item [] $det1$ \\ $n2 \vee v2$ \\ $n3 \vee v3$
\end{itemize}

Let us add two rules
\begin{itemize}
\item [] \texttt{REMOVE v IF -1 det} \\ \texttt{REMOVE n IF -1 n}
\end{itemize}

Instead of applying these rules

The condition of being unambiguously tagged becomes less necessary as well.
We add many clauses, knowing that some of them end up being false.

@@

\subsection{Other experiments}

Different strategies for maximising: ...

Modifications to an existing CG to better disambiguate with our implementation

Flipping rules: 
\begin{itemize}
\item [] \texttt{REMOVE v IF -1 det} \\ $\rightarrow$ \texttt{REMOVE det IF 1 verb}   
\item [] \texttt{REMOVE adv IF NOT 1C adj} \\ $\rightarrow$ \texttt{REMOVE (*) - Adj  IF -1 adv}  \\
\end{itemize}

With this experiment, we move even further away from a direct ``if this then that'' model of CG.
% Not really CG anymore , but

\section{Results and evaluation}

@@

% Do not number the acknowledgment section. Do not include this section
% when submitting your paper for review.
% Francis Tyers
